DNS study of turbulent pipe flow with imposed radial rotation

### 2024-12-17 paper.tex
upload 17 dic 2024

\definecolor{green}{rgb}{0.0, 0.5019607843137255, 0.0}
\definecolor{cyan}{rgb}{0.0, 1.0, 1.0}
\definecolor{orange}{rgb}{1.0, 0.6470588235294118, 0.0}
\definecolor{red}{rgb}{1.0, 0.0, 0.0}
\definecolor{purple}{rgb}{0.5019607843137255, 0.0, 0.5019607843137255}
\definecolor{black}{rgb}{0.0,0.0,0.0}
\definecolor{magenta}{rgb}{1.0,0.0,1.0}
\definecolor{blue}{rgb}{0.0,0.0,1.0}

@@

	\begin{figure}
		\centering
		\includegraphics[width=0.5\textwidth]{Figures/Pipe_spinning.pdf}
		\caption{
			Definition of coordinate system for DNS of rotating pipe flow.
			$z, r, \theta$ are the axial, radial and azimuthal coordinates, respectively. 
			$R$ is the pipe radius, $L_z$ the pipe
			length, and $u_b$ is the bulk velocity. 
			$\mathbf{\Omega}$ is the angular velocity, and
			$\mathbf{F}_c$ is the resultant mean Coriolis force.
			\textcolor{blue}{The Cartesian coordinates $x_1,x_2$ define positions in the cross-stream plane.}}
			\label{fig:sketch} 
	\end{figure}

	 	\begin{table}
	 	\begin{center}
	 		\def~{\hphantom{0}}  
	 		\begin{tabular}{cccccccc}
	 			\toprule 
	 			$\Rey_b$ & $\Rey_\tau$ & $N$ & $N_z \times N_r \times N_\theta$ & $\lambda \times 10^{-2}$ & Line \\
	 			\midrule
	 			17000 & 508  & 0.0078125 &  $769 \times 97 \times 769$ & 2.862& - \\
	 			17000 & 512  & 0.015625  &  $769 \times 97 \times 769$ & 2.942& - \\
	 			17000 & 523  & 0.03125   &  $769 \times 97 \times 769$ & 3.030& \textcolor{green}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 538  & 0.0625    &  $769 \times 97 \times 769$ & 3.212& \textcolor{cyan}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 566  & 0.125     &  $769 \times 97 \times 769$ & 3.553& \textcolor{orange}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 610  & 0.25      &  $769 \times 97 \times 769$ & 4.120& \textcolor{red}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 642  & 0.375     &  $769 \times 97 \times 769$ & 4.576& \textcolor{purple}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 669  & 0.5       &  $769 \times 97 \times 769$ & 4.962& \textcolor{black}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 748  & 1.0       &  $769 \times 97 \times 769$ & 6.208& \textcolor{magenta}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 856  & 2.0       &  $769 \times 97 \times 769$ & 8.117& \textcolor{blue}{\rule{0.05\linewidth}{0.75mm}} \\

	 			\midrule
	 			44000  & 1405  & 0.5  & $1793 \times 165 \times 1793$ & 3.262& -\\
	 			\midrule
	 			82500  & 2379  & 0.5  & $3073 \times 244 \times 3073$ & 2.662& -\\
	 			\midrule
	 			133000 & 3634  & 0.5  & $4609 \times 328 \times 4609$ & 2.389& \textcolor{black}{\rule{0.05\linewidth}{0.75mm}}\\
	 			\bottomrule
	 		\end{tabular}
	 		\caption{Flow parameters for DNS of rotating pipe flow.
	 			The bulk Reynolds number defined as $\Rey_b = 2 R u_b/\nu$, with $R$ 
	 			the pipe radius, $u_b$ the bulk velocity and 
	 			$\nu$ the fluid kinematic viscosity.
	 			$N = \Omega R/u_b$ is the rotation number 
	 			and $N_\tau = \Omega R/u^*_{\tau}$ is the friction rotation number
	 			with the global frcition velocity.
	 			$N_z, N_r, N_\theta$ are respectively the number of grid points in the axial,
	 			radial and azimuthal direction.
	 			The global friction factor is $\lambda = 8 \tau_w^* / \rho u_b^2$, with
	 			$\tau_w^*$ the azimuthally averaged mean wall shear stress and $\rho$ the fluid density.
	 			$\Rey_{\tau} = R u^*_{\tau} / \nu$ is the friction Reynolds number,
	 			with $u^*_{\tau} = \sqrt{(\tau_w^*/\rho)}$ the mean friction velocity.
	 		} 
	 		\label{tab:runs} 
	 		\end{center}
 		\end{table}

@@

	\begin{figure}
		\centering
		(a) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0_u.png}  
		(b) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.00390625_u.png}  
		(c) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.0078125_u.png} 
		(d) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.015625_u.png}   
		(e) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.03125_u.png} \\ 
		(f) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.0625_u.png} 
		(g) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.125_u.png}  
		(h) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.1875_u.png}  
		(i) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.25_u.png}
		(j) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.5_u.png} \\
		(k) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty1.0_u.png} 
    		\\ \includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
		\caption{
			Instantaneous axial velocity contours at $\Rey_b = 17000$
			in the cross-stream plane.
			Contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The pressure side of the pipe is on the left, and the suction side is on the right
			of each sub-panel.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0.078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$
                        (g) $N = 0.25$,
                        (h) $N = 0.375$,
                        (i) $N = 0.5$,
			(j) $N = 1.0$,
                        (k) $N = 2.0$.
		    }
			\label{fig:urt_500} 
	\end{figure}
	\begin{figure}
		\centering
		(a) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0_T.png}  
		(b) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.00390625_T.png}  
		(c) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.0078125_T.png} 
		(d) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.015625_T.png} 
		(e) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.03125_T.png} \\ 
		(f) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.0625_T.png} 
		(g) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.125_T.png}  
		(h) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.1875_T.png} 
		(i) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.25_T.png} 
                (j) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.5_u.png} \\
		(k) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty1.0_T.png} 
		\\ \includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
		\caption{
			Instantaneous temperature contours at $\Rey_b = 17000$
			in the cross-stream plane.
			Contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The pressure side of the pipe is on the left, and the suction side is on the right
			of each sub-panel.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0.078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$
                        (g) $N = 0.25$,
                        (h) $N = 0.375$,
                        (i) $N = 0.5$,
			(j) $N = 1.0$,
                        (k) $N = 2.0$.
		}
		\label{fig:trt_500} 
	\end{figure}

@@

	\begin{figure}
		\centering
		(a) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0_u.png}  
                (b) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.00390625_T.png} \\
		(b) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.0078125_u.png}  
		(c) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.015625_u.png} \\
		(d) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.03125_u.png} 
                (e) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.0625_u.png} \\
                (f) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.125_u.png} 
                (g) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.1875_u.png} \\ 
		(h) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.25_u.png} 
		(i) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.5_u.png} \\
                (j) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty1.0_u.png} 
		\\ \includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
		\caption{
			Instantaneous axial velocity ($u_z/u_b$) contours at $\Rey_b = 17000$
			in an unrolled cylindrical shell at a distance
			$y^*=15$ from the wall (evaluated in the non-rotating case).
			Contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The insets in the top-right corner of each panel report magnified views of a small portion of the shell.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$,
                        (g) $N = 0.1875$,
                        (h) $N = 0.25$,
                        (i) $N = 0.5$,
                        (j) $N = 2.0$.
		}
			\label{fig:utz_500} 
	\end{figure}

	\begin{figure}
		\centering
                (a) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0_T.png}
                (b) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.00390625_T.png} \\
                (c) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.0078125_T.png} 
                (d) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.015625_T.png} \\
                (e) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.03125_T.png} 
                (f) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.0625_T.png} \\
                (f) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.125_T.png} 
                (g) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.1875_T.png} \\ 
                (h) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.25_T.png} 
                (i) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.5_T.png} \\
                jj) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty1.0_T.png} 
		\\ \includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
		\caption{
			Instantaneous temperature ($t_z/t_b$) at $\Rey_b = 17000$
			in an unrolled cylindrical shell at a distance
			$y^*=15$ from the wall (evaluated in the non-rotating case).
			Contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The insets in the top-right corner of each panel report magnified views of a small portion of the shell.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
			(b) $N = 0.078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$,
			(g) $N = 0.1875$,
                        (h) $N = 0.25$,
                        (i) $N = 0.5$,
                        (j) $N = 2.0$.
		    }
			\label{fig:ttz_3000} 
	\end{figure}

	\begin{figure}
		\centering
		(a) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0_u.png}  
		(b) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.00390625_u.png}  
		(c) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.0078125_u.png} 
		(d) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.015625_u.png} 
		(e) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.03125_u.png} \\ 
		(f) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.0625_u.png} 
		(g) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.125_u.png}  
		(h) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.1875_u.png} 
		(i) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.25_u.png} 
                (j) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.5_u.png} \\
		(k) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty1.0_u.png} 
		\\ \includegraphics[width=0.5\textwidth]{Figures/uzmean_cmap.eps}
		\caption{
			Mean axial velocity contours with 
			superposed cross-flow streamlines, at $\Rey_b = 17000$.
			Twenty-four contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The pressure side of the pipe is on the left, and the suction side is on the right
			of each sub-panel.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0.078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$
                        (g) $N = 0.25$,
                        (h) $N = 0.375$,
                        (i) $N = 0.5$,
			(j) $N = 1.0$,
                        (k) $N = 2.0$.	
		    }
			\label{fig:Urt_500} 
	\end{figure}

	\begin{figure}
                \centering
                (a) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0_T.png}
                (b) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.00390625_T.png}
                (c) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.0078125_T.png}
                (d) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.015625_T.png}
                (e) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.03125_T.png} \\
                (f) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.0625_T.png}
                (g) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.125_T.png}
                (h) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.1875_T.png}
                (i) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.25_T.png}
                (j) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.5_T.png}
                (k) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty1.0_T.png}
                \\ \includegraphics[width=0.5\textwidth]{Figures/uzmean_cmap.eps}
                \caption{
                        Mean temperature contours with
                        superposed cross-flow streamlines, at $\Rey_b = 17000$.
                        Twenty-four contour levels ranging from 0 to 1.4 are shown,
                        in colour scale from blue to red.
                        The pressure side of the pipe is on the left, and the suction side is on the right
                        of each sub-panel.
                        Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0.078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$
			(g) $N = 0.25$,
                        (h) $N = 0.375$,
                        (i) $N = 0.5$,
			(j) $N = 1.0$,
                        (k) $N = 2.0$.
                    }
                        \label{fig:Trt_500}
        \end{figure}

>>>>

\definecolor{black}{rgb}{0.0, 0.0, 0.0}
\definecolor{green}{rgb}{0.0, 0.5019607843137255, 0.0}
\definecolor{cyan}{rgb}{0.0, 1.0, 1.0}
\definecolor{orange}{rgb}{1.0, 0.6470588235294118, 0.0}
\definecolor{red}{rgb}{1.0, 0.0, 0.0}
\definecolor{purple}{rgb}{0.5019607843137255, 0.0, 0.5019607843137255}
\definecolor{magenta}{rgb}{1.0, 0.0, 1.0}
\definecolor{blue}{rgb}{0.0, 0.0, 1.0}
\definecolor{pink}{rgb}{1.0, 0.75, 0.8}
\definecolor{violet}{rgb}{0.56, 0.0, 1.0}
\definecolor{darkgreen}{rgb}{0.0, 0.392, 0.0}

@@

	\begin{figure}
		\centering
		\includegraphics[width=0.5\textwidth]{Figures/Pipe_spinning.pdf}
		\caption{
			Definition of coordinate system for DNS of rotating pipe flow.
			$z, r, \theta$ are the axial, radial and azimuthal coordinates, respectively. 
			$R$ is the pipe radius, $L_z$ the pipe
			length, and $u_b$ is the bulk velocity. 
			$\mathbf{\Omega}$ is the angular velocity, and
			$\mathbf{F}_c$ is the resultant mean Coriolis force.
			The Cartesian coordinates $x_1,x_2$ define positions in the cross-stream plane.}
			\label{fig:sketch} 
	\end{figure}

	 	\begin{table}
	 	\begin{center}
	 		\def~{\hphantom{0}}  
	 		\begin{tabular}{cccccccc}
	 			\toprule 
	 			$\Rey_b$ & $\Rey_\tau$ & $N$ & $N_z \times N_r \times N_\theta$ & $\lambda \times 10^{-2}$ & Line \\
	 			\midrule
	 			17000 & 508  & 0.0078125 &  $769 \times 97 \times 769$ & 2.862& \textcolor{green}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 512  & 0.015625  &  $769 \times 97 \times 769$ & 2.942& \textcolor{cyan}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 523  & 0.03125   &  $769 \times 97 \times 769$ & 3.030& \textcolor{orange}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 538  & 0.0625    &  $769 \times 97 \times 769$ & 3.212& \textcolor{red}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 566  & 0.125     &  $769 \times 97 \times 769$ & 3.553& \textcolor{purple}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 610  & 0.25      &  $769 \times 97 \times 769$ & 4.120& \textcolor{magenta}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 642  & 0.375     &  $769 \times 97 \times 769$ & 4.576& \textcolor{blue}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 669  & 0.5       &  $769 \times 97 \times 769$ & 4.962& \textcolor{pink}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 748  & 1.0       &  $769 \times 97 \times 769$ & 6.208& \textcolor{violet}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 856  & 2.0       &  $769 \times 97 \times 769$ & 8.117& \textcolor{darkgreen}{\rule{0.05\linewidth}{0.75mm}} \\

	 			\midrule
	 			44000  & 1405  & 0.5  & $1793 \times 165 \times 1793$ & 3.262& -\\
	 			\midrule
	 			82500  & 2379  & 0.5  & $3073 \times 244 \times 3073$ & 2.662& -\\
	 			\midrule
	 			133000 & 3634  & 0.5  & $4609 \times 328 \times 4609$ & 2.389& -\\
	 			\bottomrule
	 		\end{tabular}
	 		\caption{Flow parameters for DNS of rotating pipe flow.
	 			The bulk Reynolds number defined as $\Rey_b = 2 R u_b/\nu$, with $R$ 
	 			the pipe radius, $u_b$ the bulk velocity and 
	 			$\nu$ the fluid kinematic viscosity.
	 			$N = \Omega R/u_b$ is the rotation number 
	 			and $N_\tau = \Omega R/u^*_{\tau}$ is the friction rotation number
	 			with the global frcition velocity.
	 			$N_z, N_r, N_\theta$ are respectively the number of grid points in the axial,
	 			radial and azimuthal direction.
	 			The global friction factor is $\lambda = 8 \tau_w^* / \rho u_b^2$, with
	 			$\tau_w^*$ the azimuthally averaged mean wall shear stress and $\rho$ the fluid density.
	 			$\Rey_{\tau} = R u^*_{\tau} / \nu$ is the friction Reynolds number,
	 			with $u^*_{\tau} = \sqrt{(\tau_w^*/\rho)}$ the mean friction velocity.
	 		} 
	 		\label{tab:runs} 
	 		\end{center}
 		\end{table}

@@

	\begin{figure}
		\centering
		(a) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0_u.png}  
		(b) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.00390625_u.png}  
		(c) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.0078125_u.png} 
		(d) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.015625_u.png}   
		(e) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.03125_u.png} \\ 
		(f) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.0625_u.png} 
		(g) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.125_u.png}  
		(h) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.1875_u.png}  
		(i) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.25_u.png}
		(j) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.5_u.png} \\
		(k) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty1.0_u.png} 
    		\\ \includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
		\caption{
			Instantaneous axial velocity contours at $\Rey_b = 17000$
			in the cross-stream plane.
			Contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The pressure side of the pipe is on the left, and the suction side is on the right
			of each sub-panel.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$
                        (g) $N = 0.25$,
                        (h) $N = 0.375$,
                        (i) $N = 0.5$,
			(j) $N = 1.0$,
                        (k) $N = 2.0$.
		    }
			\label{fig:urt_500} 
	\end{figure}
	\begin{figure}
		\centering
		(a) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0_T.png}  
		(b) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.00390625_T.png}  
		(c) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.0078125_T.png} 
		(d) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.015625_T.png} 
		(e) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.03125_T.png} \\ 
		(f) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.0625_T.png} 
		(g) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.125_T.png}  
		(h) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.1875_T.png} 
		(i) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.25_T.png} 
                (j) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.5_T.png} \\
		(k) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty1.0_T.png} 
		\\ \includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
		\caption{
			Instantaneous temperature contours at $\Rey_b = 17000$
			in the cross-stream plane.
			Contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The pressure side of the pipe is on the left, and the suction side is on the right
			of each sub-panel.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0.0078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$
                        (g) $N = 0.25$,
                        (h) $N = 0.375$,
                        (i) $N = 0.5$,
			(j) $N = 1.0$,
                        (k) $N = 2.0$.
		}
		\label{fig:trt_500} 
	\end{figure}

@@

	\begin{figure}
		\centering
		(a) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0_u.png}  
                (b) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.00390625_T.png} \\
		(b) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.0078125_u.png}  
		(c) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.015625_u.png} \\
		(d) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.03125_u.png} 
                (e) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.0625_u.png} \\
                (f) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.125_u.png} 
                (g) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.1875_u.png} \\ 
		(h) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.25_u.png} 
		(i) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.5_u.png} \\
                (j) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty1.0_u.png} 
		\\ \includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
		\caption{
			Instantaneous axial velocity ($u_z/u_b$) contours at $\Rey_b = 17000$
			in an unrolled cylindrical shell at a distance
			$y^*=15$ from the wall (evaluated in the non-rotating case).
			Contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The insets in the top-right corner of each panel report magnified views of a small portion of the shell.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$,
                        (g) $N = 0.1875$,
                        (h) $N = 0.25$,
                        (i) $N = 0.5$,
                        (j) $N = 2.0$.
		}
			\label{fig:utz_500} 
	\end{figure}

	\begin{figure}
		\centering
                (a) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0_T.png}
                (b) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.00390625_T.png} \\
                (c) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.0078125_T.png} 
                (d) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.015625_T.png} \\
                (e) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.03125_T.png} 
                (f) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.0625_T.png} \\
                (f) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.125_T.png} 
                (g) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.1875_T.png} \\ 
                (h) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.25_T.png} 
                (i) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.5_T.png} \\
                jj) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty1.0_T.png} 
		\\ \includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
		\caption{
			Instantaneous temperature ($t_z/t_b$) at $\Rey_b = 17000$
			in an unrolled cylindrical shell at a distance
			$y^*=15$ from the wall (evaluated in the non-rotating case).
			Contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The insets in the top-right corner of each panel report magnified views of a small portion of the shell.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
			(b) $N = 0.0078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$,
			(g) $N = 0.1875$,
                        (h) $N = 0.25$,
                        (i) $N = 0.5$,
                        (j) $N = 2.0$.
		    }
			\label{fig:ttz_3000} 
	\end{figure}

	\begin{figure}
		\centering
		(a) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0_u.png}  
		(b) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.00390625_u.png}  
		(c) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.0078125_u.png} 
		(d) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.015625_u.png} 
		(e) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.03125_u.png} \\ 
		(f) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.0625_u.png} 
		(g) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.125_u.png}  
		(h) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.1875_u.png} 
		(i) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.25_u.png} 
                (j) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.5_u.png} \\
		(k) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty1.0_u.png} 
		\\ \includegraphics[width=0.5\textwidth]{Figures/uzmean_cmap.eps}
		\caption{
			Mean axial velocity contours with 
			superposed cross-flow streamlines, at $\Rey_b = 17000$.
			Twenty-four contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The pressure side of the pipe is on the left, and the suction side is on the right
			of each sub-panel.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$
                        (g) $N = 0.25$,
                        (h) $N = 0.375$,
                        (i) $N = 0.5$,
			(j) $N = 1.0$,
                        (k) $N = 2.0$.	
		    }
			\label{fig:Urt_500} 
	\end{figure}

	\begin{figure}
                \centering
                (a) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0_T.png}
                (b) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.00390625_T.png}
                (c) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.0078125_T.png}
                (d) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.015625_T.png}
                (e) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.03125_T.png} \\
                (f) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.0625_T.png}
                (g) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.125_T.png}
                (h) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.1875_T.png}
                (i) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.25_T.png}
                (j) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.5_T.png}
                (k) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty1.0_T.png}
                \\ \includegraphics[width=0.5\textwidth]{Figures/uzmean_cmap.eps}
                \caption{
                        Mean temperature contours with
                        superposed cross-flow streamlines, at $\Rey_b = 17000$.
                        Twenty-four contour levels ranging from 0 to 1.4 are shown,
                        in colour scale from blue to red.
                        The pressure side of the pipe is on the left, and the suction side is on the right
                        of each sub-panel.
                        Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$
			(g) $N = 0.25$,
                        (h) $N = 0.375$,
                        (i) $N = 0.5$,
			(j) $N = 1.0$,
                        (k) $N = 2.0$.
                    }
                        \label{fig:Trt_500}
        \end{figure}
